---
title: "R-Programming Lab \t : Assignment 2  "
output:
  html_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
```


\newpage
***
**Question1**

Find the minimum of the function **f(x)=0.65-(0.75/(1+x^2))-0.65*x*atan(1/x)**  
using Newton's method.

**Defining function**

**f(x)**
```{r}
func <- function(x) {
  
  0.65-(0.75/(1+x^2))-0.65*x*atan(1/x)
  
}
```

**f'(x)**<-first derivative of f(x) 
```{r}
func1<- function(x) {
  (1.5*(x/(1+x^2)^2))+0.65*x/(1+x^2)-0.65*atan(1/x)
}

```


**f"(x)**<-Second derivative of  f(x) 
```{r}

func2 <- function(x) {
  (1.5*(1-3*x^2)/(1+x^2)^3)+0.65/(1+x^2)+0.65*(1-x^2)/(1+x^2)^2
}


```

**func1 is first derivative of func(or f(x) )**  
**func2 is Second derivative of func(or f(x) )**






**choosing randomly 100 guess and tolerance is 0.00001**

```{r}
guess <-seq(0.005,0.5,0.005) #100 guess
tolerance <- .00001     #tolerance

```

\newline
```{r}
cat("randomly chosen guess is:\n",guess)
```

\newpage
***

**code of newton raphson for finding minima of function**

```{r}

root <- function(func1,func2, guess, tolerance) {
  x = guess
  while (abs(func1(x)) > tolerance) {
    x = x - func1(x)/func2(x)
  }
  return(x)
}

```

**Finding minima of function for 100 points**  
for finding minima of function using newton raphson method we need one guess
(one arbitaray point )
```{r}

minima<-0
for(i in 1:100){
  x=guess[i]
  minima[i]<-root(func1,func2,x,tolerance)
}

  
```




**minimum value of f(x)**
```{r}
minima
```




**Value of function f(x) at minima (x=0.48)**
```{r}
func(minima)
```

\newpage
***
**using inbuilt function(newtonRaphson)**

**Finding minima function using library function**



```{r}

library(pracma)

out<-0  

for(i in 1:100){
  x=guess[i]
  out[i]<-newtonRaphson(func1,x,tol=0.00001)$root
  
  
}
```


**minimum value of f(x) **

```{r}
out
```


**Value of function f(x) at mimima (using inbuilt function)**
```{r}
func(out)
```


\newpage
***

**Solution Agreement with library function**

```{r}
own_ans<-func(minima)
lib_ans<-func(out)


```



```{r}
data.frame(own_ans,lib_ans)
```

from above dataframe you can observe that the data in column 1(own_ans) is exactly equal to column 2(lib_ans) as expected.

